Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published.

### 2023-06-01 paper.Rmd
final updates based on feedback

---
title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "QUANTIFYING THE FILEDRAWER FOR REGISTERED STUDIES"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/. We would like the thanks Stephen Lindsay, Cristian Mesquida Caldentey, and Henry Wyneken for feedback on a draft. 
abstract: |
  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared. Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62%) were published. We estimate that 5550 out of 9544 (58%) registrations on the OSF are published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our study shows that a substantial amount of data that researchers collect is never publicly shared.

@@

The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010]. For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81% and 66% were published, respectively [@dickersin_factors_1992]. In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.

@@

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions. How often do researchers voluntarily share information about their study, even when the study remains unpublished? And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?  Answers to these questions can provide insights into the benefits of a platform that makes registrations public after a certain time (e.g., OSF), compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

Our third question concerns the possibility to correctly identify whether a registered study is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.

@@

*Data sources*: As registrations become public after four years, we downloaded all information that can be retrieved through the application programming interface (API) of the OSF for 17.729 registrations that were created before November 18, 2017 (four years before the start of this study). Registrations are part of at least one associated project page on the OSF. Sometimes researchers still work on projects four years after a registration, and we saw continued activity in some registrations in our sample. The final classification was based on whether the projects were public in April 2022. For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project was private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy increased the probability that studies with multiple registrations were included in the study.

@@

*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years ). The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF registrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

*Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021]. We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail). We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. Our definition of ‘published’ is broader than in previous inception cohort studies (e.g., @dickersin_factors_1992; @franco_publication_2014). We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

*Identifying Publications Corresponding to Registrations*: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published. We remained uncertain when, for example, there was very little information in the preregistration, and the information that was available seemed related to a paper without a link to an OSF registration.

@@

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The `r contacted_researchers_per_publication_status$sum[3] - responses_per_publication_status$sum[3]` non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the `r contacted_researchers_per_publication_status$sum[4] - responses_per_publication_status$sum[4]` non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published.

@@

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]). Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations. Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100*result_population[4], 2)`%, of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy were classified as manually opened by the researchers have been published. In the remaining `r 100-round(100*result_manual[4], 2)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that `r round(100*result_auto[4], 2)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 2)`] of automatically opened registrations is published. Consequently, `r 100-round(100*result_auto[4], 2)`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

@@

According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.

@@

Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.

The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Better time-management, designing projects from the outset in a way that they can be completed by other team members, or making unfinished projects available to potential collaborators could mitigate these issues. The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public [@bottesini_what_2022; @pickett_questionable_2017]. It is possible that the  absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014]. If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature [@schmidt_shall_2009], and if null-results remain unreported effect size estimates in meta-analyses will be inflated [@egger_bias_1997].

@@

At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies. Our study demonstrates that the percentage of unpublished studies can be high. The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.  Empirically examining the size of the file drawer can determine if there is room for improvement.

@@

*Recommendations for Registry Users*. Researchers should be aware that the OSF only makes the registration public, but not the main project page. This means that, for example, in the “OSF-Standard Pre-Data Collection Registration” the only information that becomes visible is the answer to the question “Has data collection begun for this project?”, the answer to the question “Have you looked at the data?”, and the text in the field “Other comments”. Some users wrote in this field “See the preregistration document specifying the logic, hypotheses, and analyses” but that files is not made accessible. If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the “Other comments” field. It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration [@akker_effectiveness_2023] and to create machine-readable analysis code that describes when statistical hypotheses are corroborated or falsified [@lakens_improving_2021]. Finally, it would be useful if researchers include contact information such that peers can reach out to them with inquiries about the study that was performed. Adding an ORCID ID (for example to your OSF profile) and an email address (while realizing that researchers do not stay at the same institution indefinitely) is good practice.

@@

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large [@dickersin_factors_1992]. What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer. Researchers might find it uncomfortable to honestly discuss this topic because unpublished studies are strongly associated with bias, but our results suggest that logistical issues are a more likely reason for non-publication. More transparency about unpublished studies would allow our field to learn where we can improve how we work, thereby increasing the efficiency of psychological science.

>>>>

---
title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "QUANTIFYING THE FILEDRAWER FOR REGISTERED STUDIES"
author: 
  - name          : "Eline N. F. Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. A computationally reproducible manuscript is available at https://github.com/Lakens/registered_published and data and materials on https://osf.io/8uqfb/. We are grateful to Stephen Lindsay, Cristian Mesquida Caldentey, Henry Wyneken, and Gerda Wyssen for feedback on a draft. 
abstract: |
  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but not shared within at least 4 years. Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62%) were published. We estimate that 5550 out of 9544 (58%) registrations on the OSF are published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our study shows that a substantial amount of data that researchers collect is never publicly shared.

@@

The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010]. For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81% and 66% were published, respectively [@dickersin_factors_1992]. In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 experiments 45% were published in a scientific journal or as a book chapter, 29% were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.

@@

Second, we were interested in whether the policies of a study registry to automatically open registrations after an embargo increases the number of performed studies that become known to peers, compared to registries where registrations can remain closed indefinitely. By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions. How often do researchers voluntarily share information about their study, even when the study remains unpublished? And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?  Answers to these questions can provide insights into the benefits of a platform that makes registrations public after an embargo period (e.g., OSF), compared to platforms where users can choose to make their registration public or not (e.g., AsPredicted.org).

Our third question concerns the possibility for fellow researchers can use registries to discover unpublished studies by identifying whether a registered study is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.

@@

*Data sources*: As registrations become public after four years, we downloaded all information that can be retrieved through the application programming interface (API) of the OSF for 17.729 registrations that were created before November 18, 2017 (four years before the start of this study). Registrations are part of at least one associated project page on the OSF. Sometimes researchers still work on projects four years after a registration, and we saw continued activity in a few registrations in our sample. The final classification was based on whether the projects were public in April 2022. For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project was private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy increased the probability that studies with multiple registrations were included in the study.

@@

*Classifying Registrations*: We aimed to examine at least 300 registrations (150 for which the registration was made public by the researchers, and 150 for which the registration was made public automatically after four years). We had no justification for our sample size given uncertainty about the number of studies that would fit our inclusion criteria but relied on an informal trade-off between time constraints and sufficiently accurate estimates. The OSF API does not provide information about how a project has been made public. To circumvent this limitation, we relied on a proxy indicator to classify projects as opened by the user, or opened automatically when the embargo was lifted. We classified OSF registrations as made public by the researcher when any of the associated OSF project pages was public, and classified the project as made public automatically by the OSF after four years when the associated project page was not made public. Our reasoning is that when only the registration is public, but the underlying project remains closed, the registration is most likely opened automatically, as there are not that many use-cases where a researcher would open the registration, but not the associated project. This is not a perfect proxy, as it is possible for users to make a registration public, but to keep the associated OSF project hidden (for example, because they mistakenly believe they made the entire project public when making the registration public). When the registration and underlying project are public, we assume the registration is opened by the researchers. This assumption is more likely to hold, as only users can make underlying project pages public.

*Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021]. We considered a study ‘published’ if the study was communicated in a way that allows other researchers to learn about the results. In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail). We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. Our definition of ‘published’ is broader than in previous inception cohort studies (e.g., @dickersin_factors_1992; @franco_publication_2014). We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

*Identifying Publications Corresponding to Registrations*: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information (see the supplement for details on how much information registrations contained), and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published. We remained uncertain when, for example, there was very little information in the preregistration, and the information that was available seemed related to a paper without a link to an OSF registration.

@@

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The `r contacted_researchers_per_publication_status$sum[3] - responses_per_publication_status$sum[3]` non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the `r contacted_researchers_per_publication_status$sum[4] - responses_per_publication_status$sum[4]` non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under this latter (more conservative) assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published.

@@

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of `r sum(included_after$sum_after)` included registrations, `r result_total$x` registered studies are published (`r round(100*result_total[4], 2)`%, 95% CI [`r round(100*result_total[5], 2)`; `r round(100*result_total[6], 2)`]). Our sample contained an almost equal number of manually opened and automatically opened registrations to examine our research question about the consequences of automatically opening registrations after an embargo. As can be seen in Table \@ref(tab:table-estimated-nonpublication) manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations. Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that `r estimated_nonpublication[3,6]` registrations are published, and `r estimated_nonpublication[3,7]` remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that `r round(100*result_population[4], 2)`%, of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that `r round(100*result_manual[4], 2)`%, 95% CI [`r round(100*result_manual[5], 2)`; `r round(100*result_manual[6], 2)`] of all registrations that based on our proxy were classified as manually opened by the researchers have been published. In the remaining `r 100-round(100*result_manual[4], 2)`% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that `r round(100*result_auto[4], 1)`%, 95% CI [`r round(100*result_auto[5], 2)`; `r round(100*result_auto[6], 1)`] of automatically opened registrations is published. Consequently, `r 100-round(100*result_auto[4], )`% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

@@

According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. Only twice did researchers respond that the project was still in progress, which suggests most projects will not appear in the future, but we did see ongoing research activity in a small number of projects.

@@

Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 1)`%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009].

The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Better time-management, designing projects from the outset in a way that they can be completed by other team members, or making unfinished projects available to potential collaborators could mitigate these issues. The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public [@bottesini_what_2022; @pickett_questionable_2017]. It is probable that the  absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014]. If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature [@schmidt_shall_2009], and if null-results remain unreported effect size estimates in meta-analyses will be inflated [@egger_bias_1997].

@@

At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. It should be noted that In fields where results of studies have a high probability of becoming known (e.g., through a requirement to update registrations with the outcome), researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies. Our study demonstrates that the percentage of unpublished studies can be high. The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role. Empirically examining the size of the file drawer can determine if there is room for improvement.

@@

*Recommendations for Registry Users*. Researchers should be aware that the OSF only makes the registration public, but not the main project page. This means that, for example, in the “OSF-Standard Pre-Data Collection Registration” the only information that becomes visible is the answer to the question “Has data collection begun for this project?”, the answer to the question “Have you looked at the data?”, and the text in the field “Other comments”. Some users wrote in this field “See the preregistration document specifying the logic, hypotheses, and analyses” but those files are not made accessible when the registration is made public after four years. If researchers want to use registrations to inform peers about a study they have performed, they will need to provide all relevant information in the “Other comments” field. It is recommended to follow a comprehensive preregistration template to increase the quality of the preregistration [@akker_effectiveness_2023] and to create machine-readable analysis code that describes when statistical hypotheses are corroborated or falsified [@lakens_improving_2021]. Finally, it would be useful if researchers include contact information such that peers can reach out to them with inquiries about the study that was performed. Adding an ORCID ID (for example to your OSF profile) and an email address (while realizing that researchers do not stay at the same institution indefinitely) is good practice.

@@

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large [@dickersin_factors_1992]. What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer. Researchers might find it uncomfortable to honestly discuss this topic because unpublished studies are strongly associated with bias, but our results suggest that logistical issues are a more likely reason for non-publication. More transparency about unpublished studies would allow academics to learn where they can improve the way they work, thereby increasing the efficiency of scientific research.

### 2023-06-01 supplement.Rmd
final updates based on feedback

---
title             : "Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "SUPPLEMENT"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
abstract: |
  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.

@@

# Extensiveness of the details in registrations

@@

# Fine-grained categorization of reasons for non-publication

In the main text we have classified the reasons that researchers provided to not to publish their registered study in five categories. Below in Table \@ref(tab:reasons-non-publish) we provide a more fine-grained classification consisting of 15 categories.

@@

reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(a = sum(reason_if_unpublished == 1), b = sum(reason_if_unpublished == 2), c = sum(reason_if_unpublished == 3), d = sum(reason_if_unpublished == 4), e = sum(reason_if_unpublished == 5), f = sum(reason_if_unpublished == 6), h = sum(reason_if_unpublished == 7), i = sum(reason_if_unpublished == 8), j = sum(reason_if_unpublished == 9), k = sum(reason_if_unpublished == 10), l = sum(reason_if_unpublished == 11), m = sum(reason_if_unpublished == 12), n = sum(reason_if_unpublished == 13), o = sum(reason_if_unpublished == 14), p = sum(reason_if_unpublished == 15), q = sum(reason_if_unpublished == 16))
reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
reasons_table <- as.data.frame(reasons_table[,-1])
rownames(reasons_table) <- c("Manually Opened", "Automatically Opened", "Total")
colnames(reasons_table) <- c("No significant results", "Left academia", "Paper rejected", "Failed replication", "Unfinished study", "Educational project", "Pilot", "Switched job / research directions", "Shared with funder (not the goal to publish)", "Lack of time / busy with other projects", "Conflicting / unclear results", "Flaws in procedure", "Still in progress", "Reviewers requested it", "Extra study (no priority)", "Health issues")

@@

\newpage

>>>>

---
title             : "Supplement to: An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "SUPPLEMENT"
author: 
  - name          : "Eline N. F. Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/.
abstract: |
  This supplement provides additional details on the classification of registrations as research studies or not, the classification of studies as published or not, additional analyses about how extensive registrations were, and a more fine-grained overview of reasons researchers provided not to publish their study.

@@

# Extensiveness of Information in Registrations

@@

# Fine-Grained Categorization of Reasons for Non-Publication

In the main text we have classified the reasons that researchers provided to not publish their registered study in five categories. Below in Table \@ref(tab:reasons-non-publish) we provide a more fine-grained classification consisting of 15 categories.

@@

reasons_table <- registration_data %>% group_by(classification) %>% summarise(a = sum(reason_if_unpublished == 1), b = sum(reason_if_unpublished == 2), c = sum(reason_if_unpublished == 3), d = sum(reason_if_unpublished == 4), e = sum(reason_if_unpublished == 5), f = sum(reason_if_unpublished == 6), h = sum(reason_if_unpublished == 7), i = sum(reason_if_unpublished == 8), j = sum(reason_if_unpublished == 9), k = sum(reason_if_unpublished == 10), l = sum(reason_if_unpublished == 11), m = sum(reason_if_unpublished == 12), n = sum(reason_if_unpublished == 13), o = sum(reason_if_unpublished == 14), p = sum(reason_if_unpublished == 15), q = sum(reason_if_unpublished == 16))
reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
reasons_table <- as.data.frame(reasons_table[,-1])
rownames(reasons_table) <- c("Manually Opened", "Automatically Opened", "Total")
colnames(reasons_table) <- c("No significant results", "Left academia", "Paper rejected", "Failed replication", "Unfinished study", "Educational project", "Pilot", "Switched job / research directions", "Shared with funder (not the goal to publish)", "Lack of time / busy with other projects", "Conflicting / unclear results", "Flaws in procedure", "Still in progress", "Reviewers requested it", "Extra study (no priority)", "Health issues")

@@
